Model matters with restricted Boltzmann machines

### 2017-03-25 presentations/amherst/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | December 20, 2016
  |
  | Slides available at <http://bit.ly/kaplan-umass>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "December 20, 2016"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

source("helpers/functions.R")
```

@@

\begin{figure}
\includegraphics[width=.6\linewidth]{images/rbm.png}
\caption{Hidden nodes are indicated by white circles and the visible nodes are indicated by blue circles.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{images/visibles_image.pdf}
\caption{Image classification using a RBM: each image pixel comprises a node in the visible layer, $\mathcal{V}$ and the output of the RBM is used to create features passed to a supervised learning algorithm.}
\end{figure}

@@

\begin{columns}[T] % align columns
\begin{column}{.48\textwidth}
\begin{itemize}
\item Stacking layers of RBMs in a deep architecture
\item Proponents claim the ability to learn "internal representations that become increasingly complex, which is considered to be a promising way of solving object and speech recognition problems" (Salakhutdinov and Hinton 2009, pp. 450).
\end{itemize}
\end{column}
\hfill
\begin{column}{.48\textwidth}
\begin{figure}
\includegraphics[width=\linewidth]{images/deep_rbm.png}
\caption{Three layer deep Boltzmann machine, with visible-to-hidden and hidden-to-hidden connections but no within-layer connections.}
\end{figure}
\end{column}
\end{columns}

@@

\begin{figure}
\includegraphics[width=.55\linewidth]{images/toyhull_top.png}
\includegraphics[width=.35\linewidth]{images/toyhull_top_2.png}
\caption{The convex hull of the "statistic space" $\mathcal{T} = \{(v_1, h_1, v_1 h_1): v_1, h_1 \in \mathcal{C}\}$ in three dimensions for a toy RBM with one visible and one hidden node for $\mathcal{C} = \{0,1\}$ (left) and $\mathcal{C} = \{-1,1\}$ (right) data encoding.}
\end{figure}

@@

#grid data
load("data/results_grid.RData")

@@

```{r models-load}
load("data/sample_images.Rdata")
load("data/params_theta.Rdata")

@@

#marginalized likelihood
load("data/fitted_models_trunc_marginal_full.Rdata")
marginal_bad <- models_bad
marginal_good <- models_good

#load trick prior
load("data/fitted_models_jing_5.8.Rdata")
trick_bad <- models_bad
trick_good <- models_good

#truncated normal
load("data/fitted_models_trunc_full.Rdata")
trunc_bad <- models_bad
trunc_good <- models_good

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | December 20, 2016
  |
  | Slides available at <http://bit.ly/kaplan-umass>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "December 20, 2016"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

source("../resources/helpers/functions.R")
```

@@

\begin{figure}
\includegraphics[width=.6\linewidth]{../resources/images/rbm.png}
\caption{Hidden nodes are indicated by white circles and the visible nodes are indicated by blue circles.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{../resources/images/visibles_image.pdf}
\caption{Image classification using a RBM: each image pixel comprises a node in the visible layer, $\mathcal{V}$ and the output of the RBM is used to create features passed to a supervised learning algorithm.}
\end{figure}

@@

\begin{columns}[T] % align columns
\begin{column}{.48\textwidth}
\begin{itemize}
\item Stacking layers of RBMs in a deep architecture
\item Proponents claim the ability to learn "internal representations that become increasingly complex, which is considered to be a promising way of solving object and speech recognition problems" (Salakhutdinov and Hinton 2009, pp. 450).
\end{itemize}
\end{column}
\hfill
\begin{column}{.48\textwidth}
\begin{figure}
\includegraphics[width=\linewidth]{../resources/images/deep_rbm.png}
\caption{Three layer deep Boltzmann machine, with visible-to-hidden and hidden-to-hidden connections but no within-layer connections.}
\end{figure}
\end{column}
\end{columns}

@@

\begin{figure}
\includegraphics[width=.55\linewidth]{../resources/images/toyhull_top.png}
\includegraphics[width=.35\linewidth]{../resources/images/toyhull_top_2.png}
\caption{The convex hull of the "statistic space" $\mathcal{T} = \{(v_1, h_1, v_1 h_1): v_1, h_1 \in \mathcal{C}\}$ in three dimensions for a toy RBM with one visible and one hidden node for $\mathcal{C} = \{0,1\}$ (left) and $\mathcal{C} = \{-1,1\}$ (right) data encoding.}
\end{figure}

@@

#grid data
load("../resources/data/results_grid.RData")

@@

```{r models-load}
load("../resources/data/sample_images.Rdata")
load("../resources/data/params_theta.Rdata")

@@

#marginalized likelihood
load("../resources/data/fitted_models_trunc_marginal_full.Rdata")
marginal_bad <- models_bad
marginal_good <- models_good

#load trick prior
load("../resources/data/fitted_models_jing_5.8.Rdata")
trick_bad <- models_bad
trick_good <- models_good

#truncated normal
load("../resources/data/fitted_models_trunc_full.Rdata")
trunc_bad <- models_bad
trunc_good <- models_good

### 2017-03-25 presentations/asu/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 11, 2017
  |
  | Slides available at <http://bit.ly/kaplan-asu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 11, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 11, 2017
  |
  | Slides available at <http://bit.ly/kaplan-asu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 11, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

### 2017-03-25 presentations/msu/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 14, 2017
  |
  | Slides available at <http://bit.ly/kaplan-msu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 14, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 14, 2017
  |
  | Slides available at <http://bit.ly/kaplan-msu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 14, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

### 2017-03-25 presentations/rice/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 23, 2017
  |
  | Slides available at <http://bit.ly/kaplan-rice>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 19, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 23, 2017
  |
  | Slides available at <http://bit.ly/kaplan-rice>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 19, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

### 2017-03-25 presentations/samsi/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 30, 2017
  |
  | Slides available at <http://bit.ly/kaplan-samsi>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 30, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 30, 2017
  |
  | Slides available at <http://bit.ly/kaplan-samsi>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 30, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

### 2017-03-25 presentations/ufl/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 2, 2017
  |
  | Slides available at <http://bit.ly/kaplan-ufl>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 2, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 2, 2017
  |
  | Slides available at <http://bit.ly/kaplan-ufl>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 2, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

### 2017-03-25 presentations/uiuc/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 7, 2017
  |
  | Slides available at <http://bit.ly/kaplan-uiuc>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 7, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 7, 2017
  |
  | Slides available at <http://bit.ly/kaplan-uiuc>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 7, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

### 2017-03-25 presentations/uva/slides.Rmd
fix stupid structure

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 19, 2017
  |
  | Slides available at <http://bit.ly/kaplan-uva>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 23, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 19, 2017
  |
  | Slides available at <http://bit.ly/kaplan-uva>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 23, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---
